Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 introduction.tex
Move to local copy

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations. 
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,PR:FitKas17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13} \XW{add more reference})
considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
\XW{state the Mahadev's result + post Mahadev's development (3 papers)}.

@@

>>>>

A complexity theoretic formulation of this problem by Gottesman in 2004~\cite{web:Aaronson} asks the possibility for an efficient classical verifier (a $\BPP$ machine) to verify the output of an
efficient quantum prover (a $\BQP$ machine).
In the absence of techniques for directly tackling this question, earlier feasibility results on this problem have been focusing on two weaker formulations. 
The first type of feasibility results (e.g.,~\cite{BFK09,arXiv:ABOEM17,PR:FitKas17,mf16}) considers the case where the $\BPP$ verifier is equipped with limited quantum power.
The second type of feasibility results (e.g,~\cite{Nat:RUV13, CGJV19, Gheorghiu_2015, HPF15})
considers a $\BPP$ verifier interacting with at least two entangled, non communicating quantum provers. 
In a recent breakthrough, Mahadev~\cite{mahadev_2018} proposed the first protocol of classical verification of quantum computation (CVQC) whose soundness is based on a widely recognized computational assumption that the learning with error (LWE) problem~\cite{JACM:Regev09} is hard for $\BQP$ machines. 
The technique invented therein has inspired many  subsequent developments of CVQC protocols with improved parameters and functionality (e.g.~\cite{FOCS:GheVid19,arXiv:AlaChiHun19,arXiv:ChiaChungYam19}). 
We refer curious readers to the survey~\cite{survey:GKK19} for details.

With the newly developed techniques, we revisit the verification of quantum computation problem from both a philosophical and a practical point of view. 
Our first observation is that the sampling version of $\BQP$ (e.g., as formulated in Aaronson~\cite

\XW{motivation: say with the development, a first question is to revisit the BQP formulation; emphasize that SampBQP is a more important question; and poses some technique difficulty. }

\XW{Another feature one hope is the blindness}

\vspace{1mm} \noindent \textbf{Contribution.}

\XW{list the main results; + comparison with all related works}

@@

\XW{then the technical contribution}

### 2020-04-15 qpip0.tex
Move to local copy

\Ethan{Half of this discussion is from Han-Hsuan}

In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gave a 4-round $\QPIP_0$ protocol to let a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
\Ethan{Mahadev's end result is QPIP0 BQP.
Two steps. One is measurement proto.
The other is combine with MF.
Break the previous sentence into two sentences accordingly. Something like the following:

Mahadev's end results in groundbreaking work 4 round protocol for BQP. At the core it is a 4 round protocol to let BQP prover commit XZ measurement to a classical machine.
}
Intuitively, the protocol allows the prover to commit to a state $\rho$ and the verifier to choose a measurement basis $h$ and learn a corresponding measurement outcome $M_{XZ}(\rho, h)$ \Ethan{Actually define this notation by cutting-pasting $h$ from verifier's input}.
We now describe the protocol while omitting the implementation details.

\Ethan{Check tone, this is intro/interface}

@@

Inputs:
\begin{itemize}
	\item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$.
	\item Prover's input: a state $\rho\in\cB^{\otimes n}$ for the verifier to measure.
	\item Verifier's input:
			a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
\end{itemize}

@@

We also mention a fact that will be useful later.
\begin{fact}
\label{lem:trivial-4-round-strategy}
   There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl{\lambda}$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
\end{fact}

@@

@@

@@

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$
	\item The prover prepares $\rho^{\otimes m}$ on inputs $1^\lambda$, $1^{1/\eps}$, and $x$. Each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, on inputs $1^\lambda$ and $\vec{h}$, as in \stepref{measure1} of $\PiMeasure$.
		It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$ as in \stepref{measure2} of $\PiMeasure$.
		It sends $\vec{y}$ to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $\vec{pk}, \vec{c}, \sigma$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

@@

\begin{theorem}\label{thm:qpip0}
	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and computational soundness. 
\end{theorem}

The intuition behind this theorem is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy. Therefore if the prover want to cheat, i.e. send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$. However, the prover is quantum, so he might create quantum correlations that let him cheat with probability more than $1/m$. To prove that such kind of cheating is impossible, we use the following partition lemma from \cite{parallelrep}, which intuitively says that there exist efficient projectors $G_{0,i}$ and $G_{1,i}$ which splits a quantum state in the prover's   internal space into a part that is rejected with high probability in the testing round of $i$-th copy and a part that is accepted with high probability.  $G_{0,i}$ and $G_{1,i}$ need to be efficient because Protocol~\ref{proto:urmila4} only gives computational indistinguishability. Once we have $G_{0,i}$ and $G_{1,i}$, we can split up the prover's internal state $\ket{\psi}$ like conditional probabilistic events. For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on fifth copy then fails the the testing round on the third copy. We split the state sub-normalized states corresponding to the prover cheating on different copies and show that the sum of probabilities corresponding to bad states can't be more than $1/m$. {The actual proof is more complicated than this sketch because the $G$'s don't commute with each other, so we need to handle the splitting carefully.}

%Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
\begin{lemma}[partition lemma (revision of Lemma 3.5 of \cite{parallelrep}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{parallelrep} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$. Property~\ref{property:partition-err} corresponds to Property~1. Property~\ref{property:partition-testing} corresponds to Property~4, with $2^{m-1}$ changes to $m-1$ because we only have $m$ possible choices of $\{c\}$. Property~\ref{property:partition-binding} corresponds to Property~5. Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.})]\label{lem:partition2}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round. Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$.  Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.

@@

  Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized. $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $pk,y$. \hannote{check}

@@

We also need the following technical lemma.
\begin{lemma}\label{lem:samp-tech}
For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
\end{lemma}
\begin{proof}
\begin{align}
    \sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
    \leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}}  \nn \\ \leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\norm{ P_z\ket{\phi}}^2}     \nn \\
    \leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
    \leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
\end{align}
where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
\Ethan{Typo on line 3?}
\end{proof}

@@

For soundness, We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.

@@

@@

By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when $c=0$. Since the prover's strartegy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding}, 
\begin{align}
    \norm{(d,z_{composite,i})-(d,z_{ideal,i})}_q \leq O(\eps)
\end{align}

@@

\begin{align}
    \norm{(d,z_{good,i})-(d,z_{ideal,i})}_q \leq O(\eps).
\end{align}

@@

\begin{align}
    \norm{(d,z_{good})-(d,z_{ideal})}_q \leq O(\eps).
\end{align}
\hannote{do we lose a factor of $m$?}
Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq \eps$ if we pick $m,T,\gamma_0=???$ \hannote{tune eps}, which implies 
\begin{align} 
    \norm{(d,z)-(d,z_{good})}_1 \leq \eps
\end{align}

Therefore by Lemma~\ref{lem:computational-triangle0}, we have  
\begin{align}
     \norm{(d,z)-(d,z_{ideal})}_q \leq O(\eps)
\end{align}
\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}

>>>>

In her groundbreaking work, Mahadev~\cite{FOCS:Mahadev18a} gives a $\QPIP_0$ protocol for $\BQP$ languages.
The core of this work is a 4-round $\QPIP_0$ protocol $\PiMeasure$ that lets a $\BQP$ machine ``commit a $XZ$ measurement" to a classical machine.
Intuitively, the prover commits to a state $\rho$, while
the verifier chooses a string $h$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit; if $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.
At the end of $\PiMeasure$, the verifier learns a measurement outcome $M_{XZ}(\rho, h)$.
We now describe the interface of $\PiMeasure$ while omitting the implementation details.

@@

\Ethan{Make sure this has the right tone as an intro/interface and isn't confusing to the uninitiated.}

Inputs:
\begin{itemize}
	\item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$.
	\item Prover's input: a state $\rho\in\cB^{\otimes n}$ for the verifier to measure.
	\item Verifier's input:
	    the measurement basis choice $h \in \{0,1\}^n$ 
\end{itemize}

@@

We also mention a fact that will be useful later.
\begin{fact}
\label{lem:trivial-4-round-strategy}
   There exist a prover strategy for $\PiMeasure$ that is accepted with probability $1-\negl(\lambda)$ \Ethan{Changed n to lambda here, see what does it affect} in the testing.
\end{fact}

@@

\Ethan{TODO move the following}

\begin{lem}[another triangle inequality for computational distance]\label{lem:computational-triangle}
Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.

If
\begin{align}
    &\norm{D_1 - D_2}_q \leq \eps   \\
    &\norm{D_4 - D_6}_q \leq \eps',
\end{align}
then
\begin{align}
   \norm{ D_3 - D_5}_q \leq \eps+\eps'
\end{align}
\end{lem}
% \begin{align}
%     D_1 &\approx_{q,\eps} D_2 \\
%     D_4 &\approx_{q,\eps'} D_6,
% \end{align}
% then
% \begin{align}
%     D_3 \approx_{q,\eps+\eps'} D_5
% \end{align}
\begin{proof}
% Since
% $$\norm{D_4 - D_6}_q \leq \eps',$$
% there exist

We prove by contradiction. Suppose that
$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
$$D_3\not\approx_{c, \eps+\eps'} D_5,$$
then there exist a quantum circuit $A$ of size $poly(n)$ such that
$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that
$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$
$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$
So
\begin{align}
    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
     > &\eps
\end{align}
This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
\end{proof}

\hannote{comp. indistinguish for subnormalized state?}
\hannote{triangle inequality}

@@

\begin{proof}
For every cheating prover $\PNaiveStar$ which aborts, consider an alternative prover $P_{alt}$ which is $\PNaiveStar$ with the following modification: on the second round of Protocol~\ref{proto:urmila4}, if $\PNaiveStar$ would abort, $P_{alt}$ switch to run the trivial strategy specified by Fact~\ref{fact:perfectly_pass_test} instead. This is possible because the message send by the verifier on the first round is classical, so the prover can recalculate everything.

By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability.
\end{proof}

@@

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ as in \stepref{naive1} of $\PiNaive$.
	\item The prover prepares $\rho^{\otimes m}$; each copy of $\rho$ is prepared as in \stepref{naive2} of $\PiNaive$.
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}=(sk_1,\ldots,sk_m)$, as in \stepref{measure1} of $\PiMeasure$.
		It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ as in \stepref{measure2} of $\PiMeasure$.
		It sends $\vec{y}$ to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
		It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ as in \stepref{measure4} of $\PiMeasure$, and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round as in \stepref{output} of $\PiMeasure$.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

@@

\begin{theorem}\label{thm:qpip0}
	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(\lambda)$ completeness error and computational soundness. 
\end{theorem}

The intuition behind this theorem is that the we send out $m$ independent copies of the naive $\QPIP_0$ and do testing on randomly chosen $m-1$ copies of them, and do Hadamard round and calculate results from the remaining one copy. Therefore if the prover want to cheat, i.e. send something not binding in the Hadamard round copy, he would be caught with probability $1-1/m$. However, the prover is quantum, so he might create quantum correlations that let him cheat with probability more than $1/m$. To prove that such kind of cheating is impossible, we use the following partition lemma from \cite{parallelrep}, which intuitively says that there exist efficient projectors $G_{0,i}$ and $G_{1,i}$ which splits a quantum state in the prover's   internal space into a part that is rejected with high probability in the testing round of $i$-th copy and a part that is accepted with high probability.  $G_{0,i}$ and $G_{1,i}$ need to be efficient because $\PiMeasure$ only gives computational indistinguishability. Once we have $G_{0,i}$ and $G_{1,i}$, we can split up the prover's internal state $\ket{\psi}$ like conditional probabilistic events. For example, $G_{0,3} G_{1,5} \ket{\psi}$ corresponds to the events of passing the testing round on fifth copy then fails the the testing round on the third copy. We split the state sub-normalized states corresponding to the prover cheating on different copies and show that the sum of probabilities corresponding to bad states can't be more than $1/m$. {The actual proof is more complicated than this sketch because the $G$'s don't commute with each other, so we need to handle the splitting carefully.}

%Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
\begin{lemma}[partition lemma; revision of Lemma 3.5 of \cite{parallelrep}\footnote{$G_{0}$ and $G_{1}$ of this version are created from doing $G$ of \cite{parallelrep} and post-select on the $th$ register being $0$ or $1$ then discard $ph,th,in$. Property~\ref{property:partition-err} corresponds to Property~1. Property~\ref{property:partition-testing} corresponds to Property~4, with $2^{m-1}$ changes to $m-1$ because we only have $m$ possible choices of $\{c\}$. Property~\ref{property:partition-binding} corresponds to Property~5. Property~\ref{property-partition-norm-sum} comes from the fact that $G_0$ and $G_1$ are post-selections of orthogonal results of the same $G$.}]\label{lem:partition2}
Let $(U_0,U)$ be a prover's strategy in a $m$-fold parallel repetition of $\PiMeasure$, where $U_0$ is how the prover generates $\vec{y}$ on the second message, and $U$ is how the prover generates $\vec{a}$ on the fourth message. Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$, which corresponds to Hadamard round on the $i$-th copy and testing round on all others. Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$. \Ethan{These $n$ probably should be $\lambda$}

@@

  Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized. $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$ and $pk,y$. \hannote{check}
  \Ethan{check whether this should be some single pk and y or the entire tuple}

@@

We also need the following technical lemma.
\begin{lemma}\label{lem:samp-tech}
For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
\end{lemma}
\begin{proof}
\begin{align}
    \sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
    \leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}}  \nn \\ \leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\norm{ P_z\ket{\phi}}^2}     \nn \\
    \leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
    \leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
\end{align}
where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
\Ethan{TODO There are typos in the proof}
\end{proof}

@@

For soundness, We begin by considering the state $\ket{\psi}$ the prover in $\PiSampZ$ holds before he receives $\vec{c}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.

@@

\Ethan{ew.}

@@

By Lemma~\ref{lem:trivial-4-round-strategy} and property~\ref{property:partition-binding} of Lemma~\ref{lem:partition2}, the above strategy is accepted with probability $1-\negl(n)$ when $c=0$. Since the prover's strartegy is also efficient, by Lemma~\ref{lem:naive-qpip0-binding}, 
\begin{align}
    (d,z_{composite,i})\approx_{c, O(\eps)}(d,z_{ideal,i})
\end{align}

@@

\begin{align}
    (d,z_{good,i})\approx_{c, O(\eps)}(d,z_{ideal,i}).
\end{align}

@@

\begin{align}
    (d,z_{good})\approx_{c, O(\eps)}(d,z_{ideal}).
\end{align}
\hannote{do we lose a factor of $m$?}
Recall that by Eq~\ref{eq:z-z-good} we have $\norm{z-z_{good}}_1 \leq \eps$ if we pick $m,T,\gamma_0=???$ \hannote{tune eps}, which implies 
\begin{align}
    (d,z)\approx_{c, O(\eps)}(d,z_{good}).
\end{align}

Therefore by Lemma~\ref{lem:computational-triangle0}, we have  
\begin{align}
     (d,z)\approx_{c, O(\eps)}(d,z_{ideal}).
\end{align}
\hannote{the composition of z ideal and triangle ineq is sketchy lol. Also need to specify different z ideal}
